---
title: "R with penguins"
author: "Tin Yan Rachel Lee"
date: "2026-09-23"
---

data: Palmer Archipelago (Antarctica) penguin data (https://allisonhorst.github.io/palmerpenguins/)

In this post, we would explore the different in mass in the penguins considering their gender and species.


```{r}
#| message: false
#| warning: false

library(tidyverse)
library(palmerpenguins)
```

Before the analysis, the data must be cleaned. Observations containing missing values are dropped.

```{r}

clean_penguins <- penguins |> 
  drop_na()

clean_penguins
```

Next, we would like to confirm if there is a mass difference between male and female penguins in general among the three species.

```{r}

mass_difference <- clean_penguins |>
  group_by(sex) |>
  summarize(mean_mass = mean(body_mass_g))

mass_difference
```

Last but not least, we create a boxplot to compare the mass between the three species. According to the figure, Gentoo is significant heavier than the other two species. The average mass of Adelie and Chinstrap are similar but the distribution of mass of Adelie is greater.

```{r}

#| label: fig-penguin-mass
#| fig-cap: "Body mass of penguins by species."

ggplot(penguins, aes(x = species, y = body_mass_g)) +
  geom_boxplot(na.rm = TRUE)
```
